### 2020-09-03 README.Rmd
export neon_export :smile:

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  cache = TRUE
)
library(neonstore)
Sys.setenv("NEONSTORE_HOME" = tempfile())
```

@@

@@

```{r}
library(neonstore)
neon_download("DP1.10003.001")

@@

```{r message=FALSE}
write.csv(raw_files, "index.csv")
neon_export("my_neondata.zip", product = "DP1.10003.001")
neon_import("my_neondata.zip")
```

@@

```{r include=FALSE}
unlink("brd_countdata.zip")
unlink("index.csv")
Sys.unsetenv("NEONSTORE_HOME")
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  cache = FALSE
)
library(neonstore)
Sys.setenv("NEONSTORE_HOME" = tempfile())
```

@@

```{r}
library(neonstore)
```

@@

```{r}
neon_download("DP1.10003.001")

@@

```{r message=FALSE}
# index list alone
write.csv(raw_files, "index.csv")

# zip archive
neon_export("my_neondata.zip", product = "DP1.10003.001")
neon_import("my_neondata.zip")
```

@@

```{r include=FALSE}
unlink("my_neondata.zip")
unlink("index.csv")
Sys.unsetenv("NEONSTORE_HOME")
```
